---
title: "code"
author: "Xige Huang, Youran Wu"
date: '2022-04-24'
output: pdf_document
---

```{r setup, message=F, warning=F, echo=F}
library(tidyverse)
library(dplyr)
library(grf)
library(caret)
library(knitr)
library(clusterGeneration)
library(randomForest)
library(mvtnorm)
library(bartCause)
library(dbarts)
library(bcf)
ggplot2::theme_set(ggplot2::theme_bw())
knitr::opts_chunk$set(fig.align = 'center', cache = TRUE, warning = FALSE,
                      message = FALSE, cache.lazy = FALSE)
```


Regarding 10 Data Generating Process:

## A

N=2000, p=50, homogeneous treatment effect $\tau = 0.5$, non-sparse X, RCT with balanced treatment/control $\mathbb{P}(Z=1)=0.5$

### BART
```{r}
source('functions.R')
ndata <- 20
rmseA_cfit <- rep(NA, ndata)
biasA_cfit <- rep(NA, ndata)
sdA_cfit <- rep(NA, ndata)
for (i in 1:ndata) {
  dataA <- datagen(N=2000, k = 50, theta= 0.5, sparse=F, random_d = T, pd = 0.5)
  A_bart_cfit <- bart_cfit(DF=dataA)
  rmseA_cfit[i] <- RMSE(A_bart_cfit$ITE, dataA$theta, na.rm=T)
  biasA_cfit[i] <- mean(abs(A_bart_cfit$ITE-dataA$theta), na.rm=T)
  sdA_cfit[i] <- sd(A_bart_cfit$ITE, na.rm=T)
}
```

```{r}
rmseA <- rep(NA, ndata)
biasA <- rep(NA, ndata)
sdA <- rep(NA, ndata)
for (i in 1: ndata) {
  dataA <- datagen(N=2000, k = 50, theta= 0.5, sparse=F, random_d = T, pd = 0.5)
  A_bart <- bart_naive(DF=dataA)
  rmseA[i] <- RMSE(A_bart$x, dataA$theta, na.rm=T)
  biasA[i] <- mean(abs(A_bart$x-dataA$theta), na.rm=T)
  sdA[i] <- sd(A_bart$x, na.rm=T)
}
```

### BART-PS

```{r}
rmseA_ps_cfit <- rep(NA, ndata)
biasA_ps_cfit <- rep(NA, ndata)
sdA_ps_cfit <- rep(NA, ndata)
for (i in 1:ndata) {
  dataA <- datagen(N=2000, k = 50, theta= 0.5, sparse=F, random_d = T, pd = 0.5)
  A_bartps_cfit <- bartps_cfit(DF=dataA)
  rmseA_ps_cfit[i] <- RMSE(A_bartps_cfit$ITE, dataA$theta,na.rm=T)
  biasA_ps_cfit[i] <- mean(abs(A_bartps_cfit$ITE-dataA$theta),na.rm=T)
  sdA_ps_cfit[i] <- sd(A_bart_cfit$ITE,na.rm=T)
}
```

```{r}
rmseA_ps <- rep(NA, ndata)
biasA_ps <- rep(NA, ndata)
sdA_ps <- rep(NA, ndata)
for (i in 1: ndata) {
  dataA <- datagen(N=2000, k = 50, theta= 0.5, sparse=F, random_d = T, pd = 0.5)
  A_bartps <- bartps_naive(DF=dataA)
  rmseA_ps[i] <- RMSE(A_bartps$x, dataA$theta, na.rm=T)
  biasA_ps[i] <- mean(abs(A_bartps$x-dataA$theta), na.rm=T)
  sdA_ps[i] <- sd(A_bartps$x, na.rm=T)
}
```

### BCF

```{r}
rmseA_bcf <- rep(NA, ndata)
biasA_bcf <- rep(NA, ndata)
sdA_bcf <- rep(NA, ndata)
for (i in 1: ndata) {
  dataA <- datagen(N=2000, k = 50, theta= 0.5, sparse=F, random_d = T, pd = 0.5)
  A_bcf <- bcf_naive(DF=dataA)
  rmseA_ps[i] <- RMSE(A_bcf, dataA$theta, na.rm=T)
  biasA_ps[i] <- mean(A_bcf-dataA$theta), na.rm=T)
  sdA_ps[i] <- sd(A_bcf, na.rm=T)
}
```

```{r}
rmseA_bcf_cfit <- rep(NA, ndata)
biasA_bcf_cfit <- rep(NA, ndata)
sdA_bcf_cfit <- rep(NA, ndata)
for (i in 1: ndata) {
  dataA <- datagen(N=2000, k = 50, theta= 0.5, sparse=F, random_d = T, pd = 0.5)
  A_bcf <- bcf_cfit(DF=dataA)
  rmseA_bcf_cfit[i] <- RMSE(A_bcf, dataA$theta, na.rm=T)
  biasA_bcf_[i] <- mean(A_bcf-dataA$theta), na.rm=T)
  sdA_ps[i] <- sd(A_bcf, na.rm=T)
}
```


```{r}
resA <- data.frame(rmseA = rmseA,
                   rmseA_cfit = rmseA_cfit,
                   rmseA_ps = rmseA_ps,
                   rmseA_ps_cfit = rmseA_ps_cfit,
                   rmseA_bcf = rmseA_bcf
                   rmseA_bcf_cfit = rmseA_bcf_cfit,
                   
                   biasA = biasA,
                   biasA_cfit = biasA_cfit,
                   biasA_ps = biasA_ps,
                   biasA_ps_cfit = biasA_ps_cfit,
                   biasA_bcf = biasA_bcf,
                   biasA_bcf_cfit = biasA_bcf_cfit,
                   
                   sdA = sdA,
                   sdA_cfit = sdA_cfit,
                   sdA_ps = sdA_ps,
                   sdA_ps_cfit = sdA_ps_cfit,
                   sdA_bcf = sdA_bcf,
                   sdA_bcf_cfit = sdA_bcf_cfit
                   )
#write.table(resA, 'resA.txt', row.names = F)
```

## B
N=2000, p=50, homogeneous treatment effect $\tau = 0.5$, sparse X, RCT with imbalanced treatment/control $\mathbb{P}(Z=1)=0.2$
```{r}
dataB <- datagen(N=2000, k = 50, theta = 0.5, sparse = T,random_d = T, pd = 0.2)
```

## C
N=2000, p=50, heterogeneous treatment effect, non-sparse X, observational
```{r}
dataC <- datagen(N=2000, k = 50, random_d = F, pd = 0.2, theta = 'het', sparse = F)
```

## D
N=2000, p=10, heterogeneous treatment effect, non-sparse X, RCT pd=0.5
```{r}
dataD <- datagen(N=2000, k = 10, random_d = T, pd = 0.5, theta = 'het', sparse = F)
```

## E
N=2000, p=10, homogenous treatment effect $\tau=0.5$, sparse X, observational
```{r}
dataE <- datagen(N=2000, k = 10, random_d = F, pd = 0.5, theta = 0.5, sparse = T)
```


## F
N=500, p=50, homogeneous treatment effect $\tau = 0.5$, non-sparse X, RCT with balanced treatment/control $\mathbb{P}(Z=1)=0.5$
```{r}
dataF <- datagen(N=500, k = 50, theta= 0.5, sparse=F, random_d = T, pd = 0.5)
```


## G
N=500, p=50, homogeneous treatment effect $\tau = 0.5$, non-sparse X, RCT with imbalanced treatment/control $\mathbb{P}(Z=1)=0.2$
```{r}
dataG <- datagen(N = 500, k = 50, theta = 0.5, sparse = F, random_d = T, pd = 0.2)
```

## H
N=500, p=50, heterogeneous treatment effect, sparse X, observational
```{r}
dataH <- datagen(N = 500, k = 50, theta = "het", sparse = T, random_d = F)
```

## I
N=500, p=10, heterogeneous treatment effect, non-sparse X, RCT pd=0.5
```{r}
dataB <- datagen(N = 500, k = 10, random_d = T, pd = 0.2, theta = 0.5, sparse = F)
```

## J
N=500, p=10, homogenous treatment effect $\tau=0.5$, sparse X, observational
```{r}
dataB <- datagen(N=500, k = 10, random_d = F, pd = 0.5, theta = "het", sparse = T)
```



```{r}
source('functions.R')
ndata <- 15
rmseB_cfit <- rep(NA, ndata)
biasB_cfit <- rep(NA, ndata)
sdB_cfit <- rep(NA, ndata)
for (i in 1:ndata) {
  dataB <- datagen(N=500, k = 10, random_d = F, pd = 0.5, theta = "het", sparse = T)
  B_bart_cfit <- bart_cfit(DF=dataB)
  rmseB_cfit[i] <- RMSE(B_bart_cfit$ITE, dataB$theta, na.rm=T)
  biasB_cfit[i] <- mean(abs(B_bart_cfit$ITE-dataB$theta), na.rm=T)
  sdB_cfit[i] <- sd(B_bart_cfit$ITE, na.rm=T)
}
```
 
```{r}
rmseB <- rep(NA, ndata)
biasB <- rep(NA, ndata)
sdB <- rep(NA, ndata)
for (i in 1: ndata) {
  dataB <- datagen(N=500, k = 10, random_d = F, pd = 0.5, theta = "het", sparse = T)
  B_bart <- bart_naive(DF=dataB)
  rmseB[i] <- RMSE(B_bart$x, dataB$theta, na.rm=T)
  biasB[i] <- mean(abs(B_bart$x-dataB$theta), na.rm=T)
  sdB[i] <- sd(B_bart$x, na.rm=T)
}
```
 
### BART-PS
 
```{r}
rmseB_ps_cfit <- rep(NA, ndata)
biasB_ps_cfit <- rep(NA, ndata)
sdB_ps_cfit <- rep(NA, ndata)
for (i in 1:ndata) {
  dataB <- datagen(N=500, k = 10, random_d = F, pd = 0.5, theta = "het", sparse = T)
  B_bartps_cfit <- bartps_cfit(DF=dataB)
  rmseB_ps_cfit[i] <- RMSE(B_bartps_cfit$ITE, dataB$theta,na.rm=T)
  biasB_ps_cfit[i] <- mean(abs(B_bartps_cfit$ITE-dataB$theta),na.rm=T)
  sdB_ps_cfit[i] <- sd(B_bart_cfit$ITE,na.rm=T)
}
```
 
 
```{r}
rmseB_ps <- rep(NA, ndata)
biasB_ps <- rep(NA, ndata)
sdB_ps <- rep(NA, ndata)
for (i in 1: ndata) {
  dataB <- datagen(N=500, k = 10, random_d = F, pd = 0.5, theta = "het", sparse = T)
  B_bartps <- bartps_naive(DF=dataB)
  rmseB_ps[i] <- RMSE(B_bartps$x, dataB$theta, na.rm=T)
  biasB_ps[i] <- mean(abs(B_bartps$x-dataB$theta), na.rm=T)
  sdB_ps[i] <- sd(B_bartps$x, na.rm=T)
}
```
 
```{r}
resB <- data.frame(rmseE = rmseB,
                   rmseE_cfit = rmseB_cfit,
                   rmseE_ps = rmseB_ps,
                   rmseE_ps_cfit = rmseB_ps_cfit,
                  
                   biasE = biasB,
                   biasE_cfit = biasB_cfit,
                   biasE_ps = biasB_ps,
                   biasE_ps_cfit = biasB_ps_cfit,
                  
                   sdE = sdB,
                   sdE_cfit = sdB_cfit,
                   sdE_ps = sdB_ps,
                   sdE_ps_cfit = sdB_ps_cfit
                   )
write.table(resB, 'resJ.txt', row.names = F)
```


